---
title: "Reproducible Pitch"
subtitle: "Course Project - Developing Data Products"
author: "Taiguara Tupinambás"
date: "September 1, 2018"
output: 
  ioslides_presentation:
      font_adjustment: -1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(imager)
library(dplyr)
library(png)
im <- load.image('./coins.png')
```

## Image Segmentation

Image segmentation methods are used to break down an image into meaningful regions.  

```{r echo=FALSE}
fig <- load.image("./imageSegmentation.png")
plot(fig, axes=FALSE)
```

## Example

We will use a greyscale coin image as an example, for which we wish to identify the coins.

For that, two models are developed: simple thresholding method with linear method and watershed.
The user can determine the number of samples and the background pixel percentage.

```{r echo=FALSE, out.width = '600px', out.height = '350px', fig.align='center'}
fig <- load.image("./userInput.png")
plot(fig, axes=FALSE)
```

## Thresholding with 10000 samples {.smaller}

```{r thresh, echo = TRUE, size='tiny'}
    d <- as.data.frame(im)
    m <- sample_n(d,10000) %>% lm(value ~ x*y,data=.) 
    im.c <- im-predict(m,d)
    out <- threshold(im.c)
    out <- clean(out,3) %>% imager::fill(7)
    plot(im,axes=FALSE); highlight(out)
```

## Watershed with 10% background pixels {.smaller}
```{r water, size="tiny", echo = TRUE}
    bg <- (!threshold(im.c,"10%")); fg <- (threshold(im.c,"90%"))
    seed <- bg+2*fg; edges <- imgradient(im,"xy") %>% enorm
    p <- 1/(1+edges); ws <- (watershed(seed,p)==1)
    ws <- bucketfill(ws,1,1,color=2) %>% {!( . == 2) }
    plot(im, axes=FALSE); out2 <- clean(ws,5)
    highlight(out2,col="green")
```
